Approximation as Differentiation

### 2025-06-03 main/higher-order.tex
First pass over type interpretation.

Suppose $\cat{C}$ a Cartesian closed category with exponential $\internalHom{X}{Y}$, evaluation morphisms
$\eval_{X,Y}$ and currying isomorphisms $\lambda_{X,Y,Z}$, and the following additional structure:
\begin{enumerate}
\item finite coproducts $(\coprod, \Zero)$;
\item a strong monad $\mathcal{L}$ (lifting) with unit $\eta_X: X \to \mathcal{L}(X)$, multiplication $\mu_X:
\mathcal{L}^2(X) \to \mathcal{L}(X)$ and strength $\mathsf{st}_{X,Y}: X \times \mathcal{L}(Y) \to
\mathcal{L}(X \times Y)$;
\item $\mu$-polynomial endofunctors given by $\muPoly_{\cat{C}}$.
\end{enumerate}
\figref{default-semantics:types} gives the interpretation of a type $\tau$ with a single free type variable as
a $\mu$-polynomial endofunctor on $\cat{C}$.

>>>>

Suppose $\cat{C}$ a Cartesian closed category with exponentials $\internalHom{X}{Y}$, evaluation morphisms
$\eval_{X,Y}$ and currying isomorphisms $\lambda_{X,Y,Z}$, and the following additional structure:
\begin{enumerate}
\item finite coproducts $(\coprod, \Zero)$;
\item a strong monad $\mathcal{L}$ (lifting) with unit $\eta_X: X \to \mathcal{L}(X)$, multiplication $\mu_X:
\mathcal{L}^2(X) \to \mathcal{L}(X)$ and strength $\mathsf{st}_{X,Y}: X \times \mathcal{L}(Y) \to
\mathcal{L}(X \times Y)$;
\item $\mu$-polynomial endofunctors given by $\muPoly_{\cat{C}}$.
\end{enumerate}
\figref{default-semantics:types} gives the interpretation of a type $\Delta \vdash \tau$ with $\length{\Delta}
= n$ as a multifunctor $\cat{C}^n \to \cat{C}$ (as an object of $\cat{C}$ in the case $n = 0$).
